Asymmetric relationships and their effects on coexistence

### 2023-08-02 paper/Paper.Rnw
small typos

%Intro to storage effects and why they might be influenced by ATAs
We indicate why it is plausible that
ATAs may influence one mechanism of coexistence in particular, storage effects, starting by conceptually reviewing 
what storage effects are \citep{Chesson_1994,Chesson_2012,Ellner_2016,Barabas_2018}. 
Storage effects allow competing species to fluctuate in abundance, without any going extinct,
by providing a relative benefit to whichever species is currently rare \citep{Chesson_2000}.
Storage effects hinge on covariation between the fluctuating quality of the environment
for a species ($E$) and the strength of competition ($C$) experienced by that species (called $EC$ covariance);
and on the assumption that no two species respond in the same way to environmental variation. Then, good environmental
conditions for a currently common species are paired with strong intraspecific competition, because of
positive $EC$ covariance and the commonness of the species. But good environmental conditions for 
a currently rare species are not as closely accompanied by strong competition because the rarity of
the species limits competitive influence. The resulting asymmetry is what provides the relative benefit to the
rare species. Storage effects can be quantified by measuring to what extent $EC$ covariance contributes to 
differences between growth rates of currently rare versus currently common species \citep{Chesson_1994,Ellner_2016}.  
ATAs may, in principle, influence storage effects simply because storage effects hinge on $EC$ covariation, 
and ATAs can be an aspect of $EC$ covariation. One scenario in which it is reasonable to imagine that
ATAs may be present in $EC$ covariation pertains to water limitation. Suppose two plants compete primarily for 
water, when water is scarce, but their niches become more differentiated when water is abundant.
Then the quality of the environment, $E$, as experienced by whichever plant i. s currently rare may only correspond closely to the 
competition, $C$, imposed on it by the currently abundant plant when water is scarce and $E$ is low.

>>>>

%Intro to storage effects and why they might be influenced by ATAs
We indicate why it is plausible that
ATAs may influence one mechanism of coexistence in particular, storage effects, starting by conceptually reviewing 
what storage effects are \citep{Chesson_1994,Chesson_2012,Ellner_2016,Barabas_2018}. 
Storage effects allow competing species to fluctuate in abundance, without any going extinct,
by providing a relative benefit to whichever species is currently rare \citep{Chesson_2000}.
Storage effects hinge on covariation between the fluctuating quality of the environment
for a species ($E$) and the strength of competition ($C$) experienced by that species (called $EC$ covariance);
and on the assumption that no two species respond in the same way to environmental variation. Then, good environmental
conditions for a currently common species are paired with strong intraspecific competition, because of
positive $EC$ covariance and the commonness of the species. But good environmental conditions for 
a currently rare species are not as closely accompanied by strong competition because the rarity of
the species limits competitive influence. The resulting asymmetry is what provides the relative benefit to the
rare species. Storage effects can be quantified by measuring to what extent $EC$ covariance contributes to 
differences between growth rates of currently rare versus currently common species \citep{Chesson_1994,Ellner_2016}.  
ATAs may, in principle, influence storage effects simply because storage effects hinge on $EC$ covariation, 
and ATAs can be an aspect of $EC$ covariation. One scenario in which it is reasonable to imagine that
ATAs may be present in $EC$ covariation pertains to water limitation. Suppose two plants compete primarily for 
water, when water is scarce, but their niches become more differentiated when water is abundant.
Then the quality of the environment, $E$, as experienced by whichever plant is currently rare may only correspond closely to the 
competition, $C$, imposed on it by the currently abundant plant when water is scarce and $E$ is low.
